---
title: "visualize_apply_strategy"
output: html_document
---

```{r trade rules, include=FALSE}

# run functions implement trade rules
source('buy_sell_function.R')

```

Trade based on yesterday's signal 


## Chart Landscape

For each strategy, each visualization shows the `Cumalative Return` , `Daily Return` and `Draw Down`.

### *Cumulative Return* 

* The cumulation of daily returns in the series in terms of a `wealth index`.  

* The wealth index (when true) starts the returns at 1 rather than 0.     

### *Draw Down*  "How Much Underwater?"

* A drawdown is the percentage change between the peak price and the lowest price (trough) of an investment.  Essentially, how much did a price drop from its peak?

                                  drawdown = peak - trough / peak
  
                                                100 - 50 / 100 = %50                                

* Example - If a stock drops from $100 to $50 and then rallies back to $100.01 or above, then the drawdown was $50 or 50% from the peak.  

* Drawdowns present a significant risk to investors when considering the uptick in share price needed to overcome a drawdown. 

* For example, it may not seem like much if a stock loses 1%, as it only needs an increase of 1.01% to recover to its previous peak. However, a drawdown of 20% requires a 25% return to reach the old peak

* **Some investors choose to avoid drawdowns of greater than 20% before cutting their losses and turning the position into cash instead.**

### *Daily Return* 

      daily profit rate = daily return (close - open / open)


###Naive Buy Rule

```{r echo=FALSE}

charts.PerformanceSummary(simple_buy,
                          main="Naive Buy Rule",
                          colorset = bluefocus)



```

### Naive vs. RSI
```{r echo=FALSE}

charts.PerformanceSummary(rsi_buy_sell, 
                          wealth.index = T,
                          main="Naive v.s. RSI")

  
```

### Naive, EMA, RSI
```{r echo=FALSE}

charts.PerformanceSummary(rsi_ema_buy_sell, 
                          main="Naive v.s. RSI v.s. EMA_RSI", 
                          wealth.index = T, # starting cumulation of returns at $1 (rather than 0)
                          colorset= (1:12))
```



