---
title: "Trade Signals Based on Chart Inspection"
output: html_document
---

```{r include=FALSE}

source('global_filters.R')
source('technical_indicators.R')

```


# Overview of Trade Signals

### Relative Strength Index (RSI)
* It is the smoothed ratio of 'average' gains over 'average' losses.
* A momentum oscillator that measures the speed and change of price movements
* Traditionally the RSI is considered overbought when above 70 and oversold when below 30.
* During strong trends, the RSI may remain in overbought or oversold for extended periods
* In an uptrend or bull market, the RSI tends to remain in the 40 to 90 range with the 40-50 zone acting as support.  
* During a downtrend or bear market the RSI tends to stay between the 10 to 60 range with the 50-60 zone acting as resistance. 
* While the RSI is decent, it is somewhat outdated as far as indicators go - more currently folks use David Varadi Oscillator (DVO)

### Bolinger Bands

* Bollinger Bands define upper and lower price range levels.
* They are plotted at a standard deviation level above and below a simple moving average of the price.
* Used in pairs, both upper and lower bands and in conjunction with a moving average.
* When the bands separate by an unusual large amount, volatility increases and any existing trend may be ending. 
* When the bands tighten (from a wide to narrow band around the price) during a period of low volatility, it raises the likelihood of a sharp price move in either direction. This may begin a trending move. 
* When the bands separate by an unusual large amount, volatility increases and any existing trend may be ending. 
* A strong trend continuation can be expected when the price moves out of the bands. However, if prices move immediately back inside the band, then the suggested strength is negated.


### Momentum Oscillator
* Momentum Oscillator is the current price divided by the price of a previous period.
* Negative values indicate negative momentum, or decreasing price
* Use the Momentum Oscillator in conjunction with additional indicators or price analysis when attempting to read overbought or oversold conditions.

### MACD
* Focus on whether there's a crossover b/t macd line and the signal line.  
* MACD crossing above zero is considered bullish, while crossing below zero is bearish.
* When the MACD line crosses from below to above the signal line, the indicator is considered bullish. The further below the zero line the stronger the signal.
* When the MACD line crosses from above to below the signal line, the indicator is considered bearish. The further above the zero line the stronger the signal.


#### Signals to Buy with MA
* If the moving average with a shorter look back period crosses OVER the longer

### Candlestick Pattern

```{r echo=FALSE}

# plot hi and low prices 
chartSeries(focal_stock,
            type="bar",
            subset='2020',
            theme=chartTheme('black'))

```

## SMA - Signal

Buy signal arises when a short-run SMA crosses from below to above a long-run SMA.

Sell signal arrises when a short-run SMA crosses from above to above a long-run SMA.


```{r echo=FALSE}

chartSeries(focal_stock_adjusted, 
                 TA=c(addVo(), 
                      addSMA(n=200,on=1,col = "blue"),
                      addSMA(n=50,on=1,col = "red")),
                 subset='2020',
                 plot = TRUE,
                 theme=chartTheme('black'))




```

## EMA - Signal

Buy signal arises when a short-run EMA crosses from below to above a long-run EMA.

Sell signal arrises when a short-run EMA crosses from above to above a long-run EMA.


```{r echo=FALSE}

chartSeries(focal_stock_adjusted, 
                 TA=c(addVo(), 
                      addEMA(n=200,on=1,col = "blue"),
                      addEMA(n=50,on=1,col = "red")),
                 subset='2020',
                 plot = TRUE,
                 theme=chartTheme('black'))
```

## Bolinger Bands

Buy signal arises when price is above the band.

Sell signal arises when price is below the band (check this!!)


```{r echo=FALSE}

chartSeries(focal_stock_adjusted, 
                 TA=c(addVo(), 
                      addBBands(n=20, sd=2)),
                 subset='2020',
                 plot = TRUE,
                 theme=chartTheme('black'))

```

## MACD

Buy signal arises when MACD crosses from below to above the signal line.

Sell signal arrises when MACD crosses from above to below the signal line.

```{r echo=FALSE}

chartSeries(focal_stock_adjusted, 
                 TA=c(addVo(), 
                      addMACD(fast = 12, slow = 26, signal = 9, type = "EMA")),
                 subset='2020',
                 plot = TRUE,
                 theme=chartTheme('black'))

```

## Bringing it All Together - Plus, More!

```{r echo=FALSE}

# line chart with indicators overlaying it
chartSeries(focal_stock_adjusted, 
                 TA=c(addVo(), 
                      addBBands(n = long_past_days, sd = 2, maType = "SMA", draw = 'bands'),
                      addMomentum(n = momentum_days),
                      addROC(n = 2),
                      addMACD(fast=short_past_days,slow=long_past_days,signal=9, type="SMA"),
                      addRSI(n=relative_strength_days,maType="SMA"),
                      addTA(df_indicators$SMA, on=1, col="gray", lty = "dotted"),
                      addTA(df_indicators$SMA.1, on=1, col="gray", lty = "dotted")),
                 subset='2020',
                 plot = TRUE,
                 theme=chartTheme('black'))
```


