---
title: "stock_explore_report"
output: html_document
---


```{r include=FALSE}
# libraries 
# library(BatchGetSymbols)
# library(dplyr)
# library(tidyverse)
# library(lubridate)
# library(tidyquant) 
# library(quantmod)


source('global_filters.R')

```

Comparison of closing prices for basket of stocks

```{r echo=FALSE, warning=TRUE}

plot_actual


```

Trend Series of closing prices for basket of stocks

```{r echo=FALSE, warning=TRUE}

plot_trend


```

Trend of daily Hi and Lo prices among basket of stocks
```{r echo=FALSE, warning=TRUE}

plot_hi_lo


```

Trend of daily buy and sell-offs among basket of stocks

```{r echo=FALSE, warning=TRUE}

plot_candle


```

Short and Long term moving averages among basket of stocks

```{r echo=FALSE, warning=TRUE}


plot_ma

```

### Price Investigation of a Single Stock of Interest


TO DO:  Suppress data output and keep charts only

```{r echo=FALSE, warning=TRUE}


plot_actual_focal


```

```{r echo=FALSE, warning=TRUE}



plot_hi_lo_focal

```









